\documentclass[a4paper]{exam}

\usepackage{amsmath,amssymb,amsthm}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{titling}

% Header and footer.
\pagestyle{headandfoot}
\runningheadrule
\runningfootrule
\runningheader{CS/MATH 113, SPRING 2025}{WC 01: \LaTeX practice and introduction to logic}{\theauthor}
\runningfooter{}{Page \thepage\ of \numpages}{}
\firstpageheader{}{}{}

% Uncomment the next line to include answers
\printanswers

\title{Weekly Challenge 01: \LaTeX\; practice and introduction to logic}
\author{Blingblong} % Replace with your student ID, e.g., xy012345
\date{CS/MATH 113 Discrete Mathematics\\Habib University\\Spring 2025}

\qformat{{\large\bf \thequestion. \thequestiontitle}\hfill}
\boxedpoints

\begin{document}
\maketitle

\begin{questions}

\titledquestion{Everythings on the table} Draw the truth table of the implication operator.

\begin{solution}
\[
\begin{array}{|c|c|c|}
\hline
P & Q & P \implies Q \\
\hline
\text{True} & \text{True} & \text{True} \\
\text{True} & \text{False} & \text{False} \\
\text{False} & \text{True} & \text{True} \\
\text{False} & \text{False} & \text{True} \\
\hline
\end{array}
\]
The implication \(P \implies Q\) is false only when \(P\) is true and \(Q\) is false.
\end{solution}

\titledquestion{Triangles!} Write the Pythagorean theorem.

\begin{solution}
The Pythagorean theorem states that for a right triangle with legs of lengths \(a\) and \(b\), and a hypotenuse of length \(c\), the relationship between the sides is given by:
\[
a^2 + b^2 = c^2
\]
\end{solution}

\titledquestion{That feeling when knee surgery is tomorrow} Consider the statement ``If Luigi was a mansplaining cat then Shrek will give you knee surgery tomorrow.'' Given that Luigi is an Italian human plumber, what can you say about the above statement?

Elaborate your answers in 2 to 3 sentences by referencing the relevant row(s) in the truth table.

\begin{solution}
The statement, “If Luigi was a mansplaining cat, then Shrek will give you knee surgery tomorrow,” is a logical implication. Given that Luigi is an Italian human plumber, the premise (“Luigi was a mansplaining cat”) is false. According to the truth table for implications, when the premise is false, the entire statement is true regardless of whether the conclusion (“Shrek will give you knee surgery tomorrow”) is true or false.).
\end{solution}

\end{questions}
\end{document}
